The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-09-24 paper.qmd
fixed pixel map palette so it isnt truncated anymore

# Make standard Palette
# set Base colours
basecols <- brewer.pal(8, name = "YlOrRd")
#breaks <- seq(0,41, length.out = 9)
breaks <- 21:29 #c(0,15,24,25,26,27,30,35,41)
names(basecols) <- seq(8)
limits <- c(10,41)

@@

show_pal <- function (colours, borders = NULL, cex_label = 1, ncol = NULL, myxlab, breaks) {
  # Set dimensions of palette
  n <- length(colours)
  ncol <- ncol %||% ceiling(sqrt(length(colours)))
  nrow <- ceiling(n/ncol)
  # make matrix with null values (if not full)
  colours <- c(colours, rep(NA, nrow * ncol - length(colours)))
  colours <- matrix(colours, ncol = ncol, byrow = TRUE)
  # set graphical parameters (?)
  old <- par(pty = "s", mar = c(0, 0, 0, 0))
  on.exit(par(old))
  size <- max(dim(colours))
  plot(c(0, size), c(0, -size), type = "n", xlab = "", ylab = "", 
      axes = FALSE)
  rect(col(colours) - 1, -row(colours) + 1, col(colours), -row(colours), 
       col = colours, border = borders)
  text(c(0,col(colours)) + c(0.2, 0.1, 0,0,0,0,0,-0.1,-0.2), -c(1,row(colours))-0.25, breaks, 
              cex = 1, col = "black")
  text(4, -1.75, myxlab ,cex = 1.5, col = "black")
}

@@

show_pal(basecols, ncol=8, borders=NA, myxlab = "Temperature", breaks = 21:29)

@@

p2a
p2b
show_pal(basecols, ncol=8, borders=NA, myxlab = "Probability Temp>27", breaks = c(0, prob_breaks[2:8], 1))
```

@@

# quantile
q_a <- my_map_data_a |> 
  as.tibble() |>
  mutate(bitemp=as.numeric(bitemp)) |>
  with(data.frame(p0.05 = qnorm(0.05, mean=bitemp, sd=sqrt(variance)),
                  p0.25 = qnorm(0.25, mean=bitemp, sd=sqrt(variance)), 
                  p0.5 = qnorm(0.5, mean=bitemp, sd=sqrt(variance)), 
                  p0.75 = qnorm(0.75, mean=bitemp, sd=sqrt(variance)), 
                  p0.95 = qnorm(0.95, mean=bitemp, sd=sqrt(variance))))|>
  apply(2, function(x) ifelse(x>8, 8, x)) |>
  apply(2, function(x) ifelse(x<0, 0, x))

@@

p4a <- view(pmap_a) +
  geom_path(
      data = pmap_a$bord,
      aes_string(x = 'long', y = 'lat', group = 'group'),
      colour = "white"
    )  +
  scale_fill_gradientn(colours = basecols) +
  scale_colour_gradientn(colours = basecols) +
  theme(legend.position="none")

@@

q_b <- my_map_data_b |> 
  as.tibble() |>
  mutate(bitemp=as.numeric(bitemp)) |>
  with(data.frame(p0.05 = qnorm(0.05, mean=bitemp, sd=sqrt(variance)),
                  p0.25 = qnorm(0.25, mean=bitemp, sd=sqrt(variance)), 
                  p0.5 = qnorm(0.5, mean=bitemp, sd=sqrt(variance)), 
                  p0.75 = qnorm(0.75, mean=bitemp, sd=sqrt(variance)), 
                  p0.95 = qnorm(0.95, mean=bitemp, sd=sqrt(variance))))|>
  apply(2, function(x) ifelse(x>8, 8, x)) |> #this will mess with the variance
  apply(2, function(x) ifelse(x<0, 0, x))

@@

p4b <- view(pmap_b) +
  geom_path(
      data = pmap_b$bord,
      aes_string(x = 'long', y = 'lat', group = 'group'),
      colour = "white"
    )  +
  scale_fill_gradientn(colours = basecols) +
  scale_colour_gradientn(colours = basecols) +
  theme(legend.position="none")

# Display plots and palettes
p4a
p4b
show_pal(basecols, ncol=8, borders="white", myxlab = "Temperature", breaks = 21:29)
```

>>>>

# Make palettes
longpal <- rev(colorspace::sequential_hcl(13, palette = "YlOrRd"))
basecols <- longpal[3:10]
breaks <- 21:29 
breakslong <- 18:32 
names(basecols) <- seq(8)
names(longpal) <- -1:11

@@

show_pal <- function (colours, borders = NULL, cex_label = 1, ncol = NULL, myxlab, breaks, textnudge, xlabx, xlaby) {
  # Set dimensions of palette
  n <- length(colours)
  ncol <- ncol %||% ceiling(sqrt(length(colours)))
  nrow <- ceiling(n/ncol)
  # make matrix with null values (if not full)
  colours <- c(colours, rep(NA, nrow * ncol - length(colours)))
  colours <- matrix(colours, ncol = ncol, byrow = TRUE)
  # set graphical parameters (?)
  old <- par(pty = "s", mar = c(0, 0, 0, 0))
  on.exit(par(old))
  size <- max(dim(colours))
  plot(c(0, size), c(0, -size), type = "n", xlab = "", ylab = "", 
      axes = FALSE)
  rect(col(colours) - 1, -row(colours) + 1, col(colours), -row(colours), 
       col = colours, border = borders)
  text(c(0,col(colours)) + textnudge, -c(1,row(colours))-0.25, breaks, 
              cex = 1, col = "black")
  text(xlabx, xlaby, myxlab ,cex = 1.5, col = "black")
}

@@

show_pal(basecols, ncol=8, borders=NA, myxlab = "Temperature", breaks = 21:29, textnudge = c(0.2, 0.1, 0,0,0,0,0,-0.1,-0.2), xlabx= 4, xlaby=-1.75)

@@

p2a
p2b
show_pal(basecols, ncol=8, borders=NA, myxlab = "Probability Temp>27", breaks = c(0, prob_breaks[2:8], 1), textnudge = c(0.2, 0.1, 0,0,0,0,0,-0.1,-0.2), xlabx= 4, xlaby=-1.75)
```

@@

# quantile
q_a <- my_map_data_a |> 
  as.tibble() |>
  mutate(bitemp=as.numeric(bitemp)) |>
  with(data.frame(p0.05 = qnorm(0.05, mean=bitemp, sd=sqrt(variance)),
                  p0.25 = qnorm(0.25, mean=bitemp, sd=sqrt(variance)), 
                  p0.5 = qnorm(0.5, mean=bitemp, sd=sqrt(variance)), 
                  p0.75 = qnorm(0.75, mean=bitemp, sd=sqrt(variance)), 
                  p0.95 = qnorm(0.95, mean=bitemp, sd=sqrt(variance))))

@@

p4a <- view(pmap_a) +
  geom_path(
      data = pmap_a$bord,
      aes_string(x = 'long', y = 'lat', group = 'group'),
      colour = "white"
    )  +
  scale_fill_gradientn(colours = longpal) +
  scale_colour_gradientn(colours = longpal) +
  theme(legend.position="none")

@@

q_b <- my_map_data_b |> 
  as.tibble() |>
  mutate(bitemp=as.numeric(bitemp)) |>
  with(data.frame(p0.05 = qnorm(0.05, mean=bitemp, sd=sqrt(variance)),
                  p0.25 = qnorm(0.25, mean=bitemp, sd=sqrt(variance)), 
                  p0.5 = qnorm(0.5, mean=bitemp, sd=sqrt(variance)), 
                  p0.75 = qnorm(0.75, mean=bitemp, sd=sqrt(variance)), 
                  p0.95 = qnorm(0.95, mean=bitemp, sd=sqrt(variance))))

@@

p4b <- view(pmap_b) +
  geom_path(
      data = pmap_b$bord,
      aes_string(x = 'long', y = 'lat', group = 'group'),
      colour = "white"
    )  +
  scale_fill_gradientn(colours = longpal) +
  scale_colour_gradientn(colours = longpal) +
  theme(legend.position="none")

# Display plots and palettes
p4a
p4b
show_pal(longpal, ncol=13, borders="white", myxlab = "Temperature", breaks = 19:32, textnudge = c(0.2, 0.1, 0,0,0,0,0,0,0,0,0,0,-0.1,-0.2), xlabx= 6.5, xlaby=-2.2)
```
